---
title: "Synthetic Experiments"
output: html_notebook
---

This notebook presents the different synthetic experiments exhibited in the associated paper, as well as provides examples for using the functions and distances developed throughout this project.

# 0. Loading packages and functions

Load all the different functions

```{r setup,echo=FALSE}
knitr::opts_knit$set(root.dir = '~/Dropbox/TrackingNetworkChanges')
print(paste("Working directory set to",getwd()))
source("../main.R")
print("All functions loaded.")
```



# I. Random Graph generation

Here we try generating different instances of random graphs.

```{r,fig.width=6, fig.height=2.5}
N=50
generate_realistic_adjacency(N,opts=0,args=list(),verbose=TRUE,p=0.16)
```


```{r,fig.width=6, fig.height=2.5}
generate_realistic_adjacency(N,opts=1,args=list(),verbose=TRUE,pow= 2.4)
```
```{r,fig.width=6, fig.height=2.5}
generate_realistic_adjacency(N,opts=2,args=list(),verbose=TRUE,islands.n=4,islands.size=18,islands.pin=0.2,n.inter=7)
```
```{r,fig.width=6, fig.height=2.5}

generate_realistic_adjacency(N,opts=3,args=list(),verbose=TRUE,K=10)
```



```{r,fig.width=6, fig.height=2.5}
generate_realistic_adjacency(N,opts=4,args=list(),verbose=TRUE,pm=cbind( c(0.4,0.1, 0.001), c(.1,0.2, .01),c(.001,0.01, .5)))
```
Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
